Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-02-27 revisionMemo/rev2.tex
memo edits again

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
\item \textcolor{blue}{ \emph{
The reviewer raises an important connection to the spatial literature. The types of geographic dependencies in international relations are generally monadic in nature -- civil war spreads from Rwanda to Uganda, or protest from Lebanon to Syria. With dyadic data, however, we cannot use the common geographic adjacency matrices used for normal spatial econometrics, because in dyadic data a W matrix would need to specify how dyad i,j relates to dyad k,l (for every i,j,k,l). In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern (see Plumper and Neumayer 2010 for a more in-depth discuss on spatial lags). CD: I added this as a footnote on p.10. I moved this footnote around a LOT but I think it needs to live somewhere in the simulation. It felt awkward within the text.
}}

@@

		Done: We agree with this suggestion. We have now emphasized the importance of developing theory in our discussion of the AME and Oracle comparison (p. X), as well as in the conclusion of our paper (p.Y). We agree that innovations in dependence modeling can and should speak to theoretical advancements that, like our model, take into account the important relational and interdependent nature of political processes. 

@@

		TO DO (MG): We have added an additional paragraph on pg. 18 in our discussion of Reiter and Stam which reveals...For example in this case, the finding that countries in the middle east experience more violence might lead one to more carefully examine the effects of geography or natural resources on the intiation of conflict.

@@

		Done: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach such as random effects (Reiter and Stam (2003), third-order dependencies (Weeks), precision of fixed effects estimates (Gibler).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, we believe that they are beyond the scope of this paper at this time.

>>>>

\begin{enumerate}
	\item The additive and multiplicative effects (AME) model presented in the paper allows for a better treatment of first, second and third order dependencies in the data, and account for unobserved sources of bias in the data. The presentation of the AME estimator is clear, and the simulations provide clear evidence that the model outperforms naive OLS/GLM models fitted to the same data. The paper will be of great interest to the PSRM audience and is likely to have a strong impact on future research in international relations. I do, however, have a few suggestions for revisions that will hopefully strengthen the paper’s contributions.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We thank the reviewer for their comments and suggestions.
		}}
	\end{itemize}
	\item The paper shows that the AME model performs well in comparison to the “oracle” model where all sources of dependencies in the data are accounted for, which is reassuring. Yet this comparison feels incomplete. First, the naive model is clearly misspecified given the underlying data generating process. A large number of dependencies in international relations are linked to geography. What would happen if the dependencies were modeled using spatial econometric techniques?
	\begin{itemize}
\item \textcolor{blue}{ \emph{
The reviewer raises an important connection to the spatial literature. The types of geographic dependencies in international relations are generally monadic in nature -- civil war spreads from Rwanda to Uganda, or protest from Lebanon to Syria. With dyadic data, however, we cannot use the common geographic adjacency matrices used for normal spatial econometrics, because in dyadic data a W matrix would need to specify how dyad i,j relates to dyad k,l (for every i,j,k,l). In the simulation, we do not include a spatial lag model because this would require specifying a spatial dependence pattern (see Plumper and Neumayer 2010 for a more in-depth discuss on spatial lags). \textbf{CD}: I added this as a footnote on p.10. I moved this footnote around a LOT but I think it needs to live somewhere in the simulation. It felt awkward within the text.
}}

@@

		We agree with this suggestion. We have now emphasized the importance of developing theory in our discussion of the AME and Oracle comparison (p. X), as well as in the conclusion of our paper (p.Y). We agree that innovations in dependence modeling can and should speak to theoretical advancements that, like our model, take into account the important relational and interdependent nature of political processes. 

@@

		We have added an additional interpretation of the random effects on pg. 19 in our discussion of Reiter and Stam. (``Specifically, we can see that countries such as Iraq, Israel, Egypt, and Iran are more likely to be involved in initiating or continuing conflict with other countries than the model would predict. Further, other countries such as Bhutan, Finland, and Turkmenistan are less likely to engage in conflict than the exogenous covariates in the model would suggest. In this case, the finding that countries in the middle east experience more conflict with other countries might lead one to more carefully examine the effects of geography or natural resources on the initiation of conflict.") \textbf{CD}: Likely need to re-write to link to THEORY specifically?

@@

		We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published since the year 2000, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach such as random effects (Reiter and Stam 2003), third-order dependencies (Weeks 2012), precision of fixed effects estimates (Gibler 2017).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, we believe that they are beyond the scope of this paper at this time.
